---
title: "Homework 6"
author: "Kailey Rishovd"
date: 12/09/2020
output: github_document
---

```{r setup, include= FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot.continuous.colour = "viridis", 
  ggplot.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Problem 1

```{r message=FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>%  
  mutate(
    city_state = str_c(city, state, sep = ", "), 
    victim_age = as.numeric(victim_age), 
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0, 
      disposition == "Open/No arrest"        ~ 0, 
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"), 
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with Baltimore, MD... 

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_sex + victim_race, 
    data = baltimore_df, 
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate), 
    CI_lower = exp(estimate - 1.96 * std.error), 
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities... 

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())), 
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate), 
    CI_lower = exp(estimate - 1.96 * std.error), 
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

Create a plot that shows the estimated ORs and CIs for each city... organized according to estimate OR

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Comment on plot HERE
Plot shows the ORs comparing male homicide victims to female homicide victims... relative to homicides more or less likely to be resolved by arrest
Less often that male homicide victim cases are resolved by arrest

## Problem 2

Load and clean data

```{r message=FALSE}
birthweight_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex), 
    frace = as.factor(frace), 
    malform = as.factor(malform), 
    mrace = as.factor(mrace)
  )
```

Regression model for birthweight...

#### Modeling Process

Factors the underlay birthweight based on literature search:
`babysex` `bhead` `blength` `delwt` `fincome` `frace` `gaweeks` `momage` `mrace` `parity` `pnumlbw` `pnumgsa` `ppbmi` `ppwt` `smoken` 

Take out factors that are too alike and might cause multicolinearity:
`babysex` `bhead` `blength` `delwt` `fincome` `frace` `gaweeks` `momage` `mrace` `parity` `pnumlbw` `ppbmi` `ppwt` `smoken`

```{r}
factors_of_int_df = 
  lm(bwt ~  babysex + bhead + blength + delwt + fincome + frace + gaweeks + momage + mrace + parity + pnumlbw + ppbmi + ppwt + smoken, data = birthweight_df)
```

Look at results..  

```{r}
summary(factors_of_int_df)

broom::glance(factors_of_int_df)
```

Looking at the summary of the model p-values: `fincome`, `frace`, `momage`, `mrace` 3 and 4, and `ppwt` are not significant to the model. Further, `parity` is not highly significant to the model. I will keep `mrace` because one indicator variable was significant. Additionally, `pnumlbw` does not have enough data points. In my proposed model I will exclude all of the variables mentioned above, except `mrace.` 

R square is 71.8%

```{r}
proposed_model_df = 
  lm(bwt ~ bhead + blength + mrace + delwt + gaweeks + ppbmi + smoken, data = birthweight_df)

summary(proposed_model_df)

broom::glance(proposed_model_df)
```

I removed `babysex` becuase when removing, it caused no change to the R square. 

R square is 71.7%

#### Residuals

Residuals against fitted values...

```{r}
resid_pred_p = 
  birthweight_df %>% 
    add_predictions(proposed_model_df) %>% 
    add_residuals(proposed_model_df) %>% 
    ggplot(aes(x = resid, y = pred)) +
    geom_point(alpha = .3)

resid_pred_p
```

Comparing model to two others... 

```{r}
main_effects_df = 
  lm(bwt ~ blength + gaweeks, data = birthweight_df)

broom::glance(main_effects_df)
```

```{r}
interactions_df = 
  lm(bwt ~ babysex * bhead *blength, data = birthweight_df)

broom::glance(interactions_df)
```

Cross-validated prediction error: 

```{r}
cv_birthweight_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble), 
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    proposed_mod = map(.x = train, ~lm(bwt ~ bhead + blength + mrace + delwt + gaweeks + ppbmi + smoken, data = .x)), 
    maineff_mod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)), 
    interactions_mod = map(.x = train, ~lm(bwt ~ babysex * bhead *blength, data = .x))
  ) %>%     
  mutate( 
    rmse_proposed = map2_dbl(.x = proposed_mod, .y = test, ~rmse(model = .x, data = .y)), 
    rmse_maineff = map2_dbl(.x = maineff_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_interactions = map2_dbl(.x = interactions_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

What do these results say about model choice? 

```{r}
cv_birthweight_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(), 
    names_to = "model", 
    values_to = "rmse", 
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

Compute averages... 

```{r}
cv_birthweight_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(), 
    names_to = "model", 
    values_to = "rmse", 
    names_prefix = "rmse_"
  ) %>%
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```

Model choice? 

As we can see from the violin plot, *maineff* does not have great model fit because it will not predict birthweight sufficiently. 
The *interactions* and *proposed* models see improvement from *maineff*. 


In choosing a model, the model that will best predict birthweight, from the three models compared in this assignment, is the *proposed* model. This model has the lowest average rmse (275) and the smallest distribution of errors.

## Problem 3

Import data 

```{r message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

